Investigating Item Bias 

### 2021-10-20 paper/cogsci.Rmd
outline and methods updates

- introduce importance of measuring early language development (e.g., links to later educational outcomes)
- introduce CDI
- what is a good measure? 
- IRT
- what does between-group bias look like?

- what is our goal for measuring vocabulary? - identifying language delays, predicting later reading, or talking...
- how you select items influences how well you achieve these goals (and what bias you find)

@@

We analyze American English CDI: Words & Sentences administrations from `r nrow(d_demo)` children aged `r min(d_demo$age)` to `r max(d_demo$age)` from Wordbank [@Frank2016].

@@

## Second-Level Headings

Second level headings should be 11 point , initial caps, bold, and
flush left. Leave one line space above the heading and 1/4~ line
space below the heading.

### Third-Level Headings

Third-level headings should be 10 point , initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.

# Formalities, Footnotes, and Floats

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
[-@NewellSimon1972a], but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
[@NewellSimon1972a]. List multiple references alphabetically and
separate them by semicolons [@ChalnickBillman1988a; @NewellSimon1972a]. 
Use the et. al. construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

For more information on citations in RMarkdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**

## Footnotes

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.} You can also use 
markdown formatting to include footnotes using this syntax [^1].

[^1]: Sample of a markdown footnote.

## Figures

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10 point, after the figure with one line space
above the caption and one line space below it. If necessary, leave extra white space at
the bottom of the page to avoid splitting the figure and figure
caption. You may float figures to the top or bottom of a column, or
set wide figures across both columns.

## Two-column images

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

>>>>

- introduce importance of measuring early language development (e.g., links to later educational outcomes)
- introduce CDI
- predictive validity: Fenson et al. 1994, Bornstein et al. 2012, Duff et al. 2015

- discuss potential for bias
- what does between-group bias look like?

- IRT - what is a good measure?

## Fundamental DIF Problem

- what is our goal for measuring vocabulary? - identifying language delays, predicting later reading, or talking...
- how you select items influences how well you achieve these goals (and what bias you find)
We take the approach put forward by @Stenhaug2021: GLIMMER plots based on the 1-parameter logistic are sufficient to identify bias, without potentially obscuring DIF in a more complex model's additional parameters.

@@

We analyze American English CDI: Words & Sentences administrations from `r nrow(d_demo)` children aged `r min(d_demo$age)` to `r max(d_demo$age)` from Wordbank [@Frank2016; @Frank2021].

@@

### Participants

```{r}
sex_tab <- table(d_demo$sex)

eth_tab <- table(d_demo$ethnicity)
```

We use Wordbank data from `r sex_tab["Female"]` female and `r sex_tab["Male"]` male participants, and was unreported for an additional `r sum(is.na(d_demo$sex))` participants.
<!-- same for eth, SES -->

<!-- goal: make custom glimmer plot in R with high / low bias words -->
```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```
